Likelihoods for a general class of ARGs under the SMC

### 2025-04-23 paper.tex
Address point

% % % % % % % % % % % % % % % % % %
\subsection*{Algorithm} \label{par:algo}
In this section we describe how to efficiently compute the likelihood under the SMC
from an ARG stored using the \texttt{tskit} tree sequence encoding. 
The tree sequence format encodes relationships using \emph{edges},
along with additional information that
allows us to sequentially recover (and reason about their differences) \revpoint{1}{5}
efficiently~\citep{kelleher_efficient_2016, ralph_efficiently_2020}.
The order of the edge deletions and insertions required to move from one local tree $T_1$ to
the next, $T_2$ imposes the strict total ordering on edges
(see definition~\eqref{def:coal})
that is needed to efficiently maintain the state of $I_e(t)$ for each focal edge $e$.
Indeed, following the removal of edges that do not persist in $T_2$,
we simply declare that each subsequently added edge
can only coalesce with the already-visited edges 
that make up the (partially) reconstructed local tree $T_2$.

>>>>

% % % % % % % % % % % % % % % % % %
\subsection*{Algorithm} \label{par:algo}
In this section we describe how to efficiently compute the likelihood under the SMC
from an ARG stored using the \texttt{tskit} tree sequence encoding.
The tree sequence format encodes relationships using \emph{edges},
along with additional information that
allows us to sequentially recover local trees (and reason about their differences) \revpoint{1}{5}
efficiently~\citep{kelleher_efficient_2016, ralph_efficiently_2020}.
The order of the edge deletions and insertions required to move from one local tree $T_1$ to
the next, $T_2$ imposes the strict total ordering on edges
(see definition~\eqref{def:coal})
that is needed to efficiently maintain the state of $I_e(t)$ for each focal edge $e$.
Indeed, following the removal of edges that do not persist in $T_2$,
we simply declare that each subsequently added edge
can only coalesce with the already-visited edges
that make up the (partially) reconstructed local tree $T_2$.
